Re-fit

### 2022-09-10 scripts/r/04_refit/refit_tr.Rmd
rename, refit models from pervagor_meeki so the labels correspond with google sheet

# libs
library(tidyverse)
library(brms)
library(readxl)
library(lme4)

@@

pervagor_meeki_2_f0meannoun_cat <- brm(
  Mean_f0_st_s ~ 
         effect_cat + 
         + (effect_cat | speaker),
  seed = 111,
  data = data_meanf0_trim[data_meanf0_trim$word_type == "target_name",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_2_f0meannoun_cat"
  )

pervagor_meeki_3_f0maxnoun_cat <- brm(
  Max_f0_st_s ~ 
         effect_cat + 
         + (1| speaker),
  seed = 111,
  data = data_maxf0_trim[data_maxf0_trim$word_type == "target_name",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_3_f0maxnoun_cat"
  )

pervagor_meeki_4_durnoun_cat <- brm(
  Duration_ms_s ~ 
         effect_cat + 
         + (1| speaker),
  seed = 111,
  data = data_dur_trim[data_dur_trim$word_type == "target_name",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_4_durnoun_cat"
  )

@@

pervagor_meeki_6_f0meanadj_cat <- brm(
  Mean_f0_st_s ~ 
         effect_cat + 
         + (1 | speaker)
         + (1 | target_word),
  seed = 111,
  data = data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_6_f0meanadj_cat"
  )

pervagor_meeki_7_f0maxadj_cat <- brm(
  Max_f0_st_s ~ 
         effect_cat + 
         + (1 | speaker)
         + (1 | target_word),
  seed = 111,
  data = data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_7_f0maxadj_cat"
  )

pervagor_meeki_8_duradj_cat <- brm(
  Duration_ms_s ~ 
         effect_cat + 
          + (1 | speaker)
          + (effect_cat | target_word),
  seed = 111,
  data = data_dur_trim[data_dur_trim$word_type == "target_colour",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_8_duradj_cat"
  )

>>>>

# libs
library(tidyverse)
library(brms)
library(readxl)
library(lme4)
library(here)

@@

pervagor_meeki_2_durnoun_cat <- brm(
  Duration_ms_s ~ 
         effect_cat + 
         + (1| speaker),
  seed = 111,
  data = data_dur_trim[data_dur_trim$word_type == "target_name",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_2_durnoun_cat"
  )

pervagor_meeki_3_f0meannoun_cat <- brm(
  Mean_f0_st_s ~ 
         effect_cat + 
         + (effect_cat | speaker),
  seed = 111,
  data = data_meanf0_trim[data_meanf0_trim$word_type == "target_name",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_3_f0meannoun_cat"
  )

pervagor_meeki_4_f0maxnoun_cat <- brm(
  Max_f0_st_s ~ 
         effect_cat + 
         + (1| speaker),
  seed = 111,
  data = data_maxf0_trim[data_maxf0_trim$word_type == "target_name",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_4_f0maxnoun_cat"
  )

@@

pervagor_meeki_6_duradj_cat <- brm(
  Duration_ms_s ~ 
         effect_cat + 
          + (1 | speaker)
          + (effect_cat | target_word),
  seed = 111,
  data = data_dur_trim[data_dur_trim$word_type == "target_colour",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_6_duradj_cat"
  )

pervagor_meeki_7_f0meanadj_cat <- brm(
  Mean_f0_st_s ~ 
         effect_cat + 
         + (1 | speaker)
         + (1 | target_word),
  seed = 111,
  data = data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_7_f0meanadj_cat"
  )

pervagor_meeki_8_f0maxadj_cat <- brm(
  Max_f0_st_s ~ 
         effect_cat + 
         + (1 | speaker)
         + (1 | target_word),
  seed = 111,
  data = data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",], 
  cores = 4,  
  file = "./data/analyses/models/pervagor_meeki_8_f0maxadj_cat"
  )
